### 2023-01-12 code/plots.Rmd
tidy up

```{r}
ppo <- read_csv("../data/PPO.csv")
```

@@

```{r}
msy <- read_csv("../data/msy.csv")
best <- msy |> 
  filter(t == max(t)) |> 
  group_by(action) |> summarise(reward = mean(reward)) |> 
  filter(reward == max(reward))
best
```
```{r}
msy_sim <- msy |>
  filter(action == best$action) |> 
  pivot_longer(c("sp1", "sp2", "sp3"), names_to = "species", values_to = "abundance")

>>>>

```{r}
ppo <- read_csv("../data/PPO.csv.gz")
```

@@

```{r}
msy <- read_csv("../data/msy.csv.gz")
best <- msy |> 
  filter(t == max(t)) |> 
  group_by(action) |> summarise(reward = mean(reward)) |> 
  filter(reward == max(reward))
best
```
```{r}
msy_sim <- msy |>
  filter(action == best$action) |> 
  pivot_longer(c("sp1", "sp2", "sp3"), names_to = "species", values_to = "abundance")
